Object detection for Verification Based Annotation

### 2019-09-09 paper.tex
Updates from Overleaf

\begin{itemize}
    \item {\textbf {Sharing}}\par No shared weights between classification sub-networks at different pyramid levels, to make training much faster at the beginning.
    \item {\textbf {Non normalised loss}}\par 
    We do not normalise of the loss function (by the number of anchor matches), to accommodate images with no positive annotations.
    \item {\textbf {High resolution}}\par We train on crops of high-resolution images, but for inference operate on complete images. The motivation is to make the object detection task as easy as possible; larger objects are easier to detect \cite{Lin2014}. 
    \item {\textbf {Cyclical learning rates}}\par We use of cyclical learning rates in training, to accommodate incremental additions to the training set.
    \item {\textbf{Extra decoder layers}}\par We used an extra residual block at each resolution to combine shortcut connections after concatenation with features from lower resolutions.
\end{itemize}

@@

Code for this paper can be found \href{https://github.com/saulzar/detection/tree/thesis}{here}, under the tag ``thesis'', with details surrounding the cropping procedure, default training and augmentation parameters etc.

@@

A selection of the datasets with images and annotations (as well as annotation history logs) can be found at \href{http://academictorrents.com/details/e780e1a9e898e53e72c16cb5fcc6d61d90cc4d27}{Annotated object detection datasets}.

>>>>

\begin{itemize}
    \item {\textbf {Sharing}}: no shared weights between classification sub-networks at different pyramid levels, to make training much faster at the beginning.
    \item {\textbf {Non normalised loss}}:
    We do not normalise of the loss function (by the number of anchor matches), to accommodate images with no positive annotations.
    \item {\textbf {High resolution}}: We train on crops of high-resolution images, but for inference operate on complete images. The motivation is to make the object detection task as easy as possible; larger objects are easier to detect \cite{Lin2014}. 
    \item {\textbf {Cyclical learning rates}}: We use of cyclical learning rates in training, to accommodate incremental additions to the training set.
    \item {\textbf{Extra decoder layers}}: We used an extra residual block at each resolution to combine shortcut connections after concatenation with features from lower resolutions.
\end{itemize}

@@

Code for this paper can be found \href{https://github.com/saulzar/detection/tree/thesis}{link}, under the tag ``thesis'', with details surrounding the cropping procedure, default training and augmentation parameters etc.

@@

A selection of the datasets with images and annotations (as well as annotation history logs) can be found at \href{http://academictorrents.com/details/e780e1a9e898e53e72c16cb5fcc6d61d90cc4d27}{link}.
